|

### 2024-11-08 output/seminar-slideshow.qmd
Add slide about comparison of high and low MDISCs

::::: columns
::: column
```{r mirt-model-irs-3d}
#| fig-width:  4.6
#| fig-height: 4.6
PROB_AXIS_2D <- seq(-3, 3, by = .1)

@@

<!-- # TODO: Superficies de ítems con alta y baja discriminación -->

>>>>

::::: columns
::: column
```{r mirt-model-irs-3d}
#| fig-width:  5
#| fig-height: 5
PROB_AXIS_2D <- seq(-3, 3, by = .1)

@@

```{r mdisc-items}
mdisc_items <- tribble(
  ~item, ~a_1, ~a_2, ~d,
  1,     4,    0.1,     0,
  2,     0.01, 0.02,  0,
)

mirt_item_probs <- expand_grid(
  trait_1 = PROB_AXIS_2D,
  trait_2 = PROB_AXIS_2D
) |>
  mutate(
    mdisc_items |>
      select(-item) |>
      pmap(irs2d, theta_1 = trait_1, theta_2 = trait_2) |>
      bind_cols()
  ) |>
    rename_with(str_replace, pattern = '\\.{3}', replacement = "prob_")
```

::::: columns
::: column
$$
  \mathbf{a}_1 = \begin{bmatrix}
    0.1 \\
    0.02
  \end{bmatrix};\quad
  d_1 = 0
$$

```{r low-mdisc-irs-contour}
#| fig-height: 5
#| fig-width:  5
mirt_prob_surface <- mirt_item_probs |>
  select(starts_with("trait"), prob_2) |>
  pivot_wider(names_from = trait_1, values_from = prob_2) |>
    select(-trait_2) |>
    as.matrix()

plot_ly(
  x = ~PROB_AXIS_2D,
  y = ~PROB_AXIS_2D,
  z = ~mirt_prob_surface,
  colorscale = list(c(0, 1), PALETTE_BLUE["normal"] |> rep(2)),
  type = 'surface',
  hovertemplate = 'P(I<sub>1</sub> = 1) = %{z:.2f}<extra></extra>',
  showscale = FALSE,
  hoverinfo = 'Z'
) |>
  layout(
    scene = list(
      xaxis = list(title = "<i>θ</i><sub>1</sub>"),
      yaxis = list(title = "<i>θ</i><sub>2</sub>"),
      zaxis = list(
        range = 0:1,
        title = "P(I<sub>1</sub> = 1)"
      ),
      camera = list(
        center = list(x = -.1, z = -.2),
        eye = list(x = -.12, y = -1.8, z = 1)
      )
    )
  ) |>
  config(displayModeBar = FALSE, scrollZoom = FALSE)
```
:::

::: column
$$
  \mathbf{a}_2 = \begin{bmatrix}
    4 \\
    0.1
  \end{bmatrix};\quad
  d_2 = 0
$$

```{r high-mdisc-irs-contour}
#| fig-height: 5
#| fig-width:  5
mirt_prob_surface <- mirt_item_probs |>
  select(trait_1:prob_1) |>
  pivot_wider(names_from = trait_1, values_from = prob_1) |>
    select(-trait_2) |>
    as.matrix()

plot_ly(
  x = ~PROB_AXIS_2D,
  y = ~PROB_AXIS_2D,
  z = ~mirt_prob_surface,
  colorscale = list(c(0, 1), PALETTE_BLUE["normal"] |> rep(2)),
  type = 'surface',
  hovertemplate = 'P(I<sub>2</sub> = 1) = %{z:.2f}<extra></extra>',
  showscale = FALSE,
  hoverinfo = 'Z'
) |>
  layout(
    scene = list(
      xaxis = list(title = "<i>θ</i><sub>1</sub>"),
      yaxis = list(title = "<i>θ</i><sub>2</sub>"),
      zaxis = list(
        range = 0:1,
        title = "P(I<sub>2</sub> = 1)"
      ),
      camera = list(
        center = list(x = -.1, z = -.2),
        eye = list(x = -.12, y = -1.8, z = 1)
      )
    )
  ) |>
  config(displayModeBar = FALSE, scrollZoom = FALSE)
```
:::
:::::
